\section{Leadership}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{IEEE at UCF}}{}
      {Treasurer}{April 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Managed the IEEE UCF chapter's finances, developing and tracking a \$XXXX budget across multiple projects and events, ensuring accurate allocation of resources and financial accountability.}
        \resumeItem{Secured \$XXXX in sponsorship funding through effective communication and negotiation with industry partners, directly supporting student project development and participation in competitions like South EastCon.}
        % \resumeItem{Oversaw budget planning and resource allocation for technical project teams, including the South EastCon robotics team, providing guidance on financial feasibility and ensuring projects received necessary funding for hardware, software, and development tools.}
      \resumeItemListEnd
      
    \resumeSubheadingContinue
    % \resumeSubheading
    %   {\textbf{IEEE at UCF}}{}
      {SouthEastCon Hardware/Robotics Competition Software Lead}{Sept 2024 -- April 2025}
    \resumeItemListStart
      \resumeItem{Led software pipeline for 10+ team using ROS2, enabling low-latency control between modular hardware and decision nodes. Used Gazebo and OpenCV for validation, contributing to 1st place in Design and 2nd in Performance at competition.}
      \resumeItem{Developed embedded firmware on Teensy 4.1 for sensor fusion and actuator control with modular, real-time C++ code. Optimized for high-frequency loops and low resource use, improving system responsiveness and performance.}
      % \resumeItem{Managed Git/GitHub workflows with branching strategies, code reviews, and issue tracking to ensure team-wide consistency. Built CI/CD pipelines for automated testing and deployment, and implemented HIL testing for early hardware validation.}
    \resumeItemListEnd
    
    \resumeSubheadingContinue
      {Internal Projects Competition Sublead}{Aug 2024 -- April 2025}
    \resumeItemListStart
      \resumeItem{Co-managed an internal IEEE project competition at UCF, structuring the competition and mentoring teams; organized and led workshops on GIT version control and command-line usage for Linux, Mac, and Windows, improving workflow.}
      \resumeItem{Assisted teams in securing funding and budget approvals for beginner and advanced projects; guided teams through financial planning and resource allocation while fostering collaboration, enabling successful completion.}
    \resumeItemListEnd

    % \resumeSubheadingContinue
    %   {Workshop Director}{Jan 2024 -- April 2025}
    % \resumeItemListStart
    %  \resumeItem{Designed and facilitated a Linux workshop for 30+ IEEE members, teaching core skills in software installation, file system navigation, and terminal-based program execution to enhance technical proficiency.}
    % \resumeItemListEnd

    % \resumeSubheadingContinue
    %   {Inventory Manager}{Sept 2023 -- April 2025}
    % \resumeItemListStart
    %  \resumeItem{Overhauled a 200-item inventory system using Google Sheets, implementing improved categorization and accessibility features that reduced retrieval times by over 30\% and minimized inventory discrepancies.}
    % \resumeItemListEnd

  % \resumeSubheading
  %   {\textbf{UCF Association for Computing Machinery}}{}
  %   {Treasurer}{April 2025 -- Present}
  %   \resumeItemListStart
  %     \resumeItem{IDK}
  %     \resumeItem{IDK}
  %   \resumeItemListEnd

  % \resumeSubheading
  %  {\textbf{IEEE-EMBS at UCF}}{}
  %  {Treasurer}{April 2024 -- April 2025}
  %  \resumeItemListStart
  %    \resumeItem{Managed a \$3000 budget to support project initiatives, establishing a secure bank account, creating predictive annual budgets, and tracking expenses to meet 100\% of fiscal targets.}
  %  \resumeItemListEnd

  \resumeSubHeadingListEnd
